---
title: "Handling Adjusted Rand Indices results"
author: "Edmond Sanou"
date: "02/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
source("./rscripts/mglasso_functions/onload.R")
```

# Clustering  
Settings:  
- Inter-clusters edge probability $0.01$ (flip on all the missing edges)  
- Theoretical correlations are different from empirical correlation levels in general

## Rand index  
```{r}
load(paste0(path_extended, "rand100_config_p40_bdiagflip001_allcor.RData")) 
dt <- rand100_config_p40_bdiagflip001_allcor
# Calculate clusters partitions with thresh_fuse as the required difference threshold for merging two regression vectors
list_res <- lapply(dt, function(e){get_perf_from_raw("rand", e, thresh_fuse = 1e-6)})
dt_rand <- do.call(rbind, list_res)
```

```{r}
save(dt_rand,
     file = paste0(path_extended, "dt_rand_p40_bdiagflip001_allcor_thresh_e6.RData"))
```

## Theoritical correlation set to $0.25$

```{r}
plot_res(dt_rand, crit_ = "rand", ncluster_ = c(5, 10, 15, 20), cor_ = 0.25, np_ = c(0.5, 1, 2))
```

## Theoritical correlation set to $0.95$

```{r}
plot_res(dt_rand, crit_ = "rand", ncluster_ = c(5, 10, 15, 20), cor_ = 0.95, np_ = c(0.5, 1, 2))
```

The files `rand_dt_higher_cor_sbm.RData` and `rand_dt_lower_cor_sbm.RData` are obtained from splitting `dt_rand`according to theoritical correlation levels.