---
title: "Gut data analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./rscripts/mglasso_functions/onload.R")
```

### Data Handling

Load 
```{r}
# data also available in spiec-easi package. Use `data(amgut1.filt)`
load(paste0(path_data, "amgut1.filt.rda"))
dta <- amgut1.filt
```

Transform data using `clr` approach or non paranormal method
```{r}
dta <- t(clr(dta + 1 , 1))
```

Hierarchical clustering   
```{r}
S <- cor(dta)
hclust_dta <- hclust(dist(t(dta)), method = "ward.D")
hclust_dta <- hclust(as.dist(1-S^2), method = "ward.D")

cut_dta <- cutree(hclust_dta, 4)
```

```{r}
image(S[order(cut_dta), order(cut_dta)])
```

```{r}
image(as(S[order(cut_dta), order(cut_dta)],
         "sparseMatrix"), 
      sub = "", xlab = "", ylab = "",
      colorkey = FALSE)
```

Correlation matrix for groups 
```{r}
# mean of vars in the same clusters
dta_grouped <- t(aggregate(t(dta), list(cut_dta), "mean"))
dta_grouped <- dta_grouped[-1,]

# cor mat of the meta-vars
cor_dta_grouped <- cor(dta_grouped)
cor_dta_grouped
```

Mean correlations inside blocks
```{r}
C <- cor(dta)
diag(C) <- 0
clusters <- cut_dta

seq_p <- 1:length(clusters)
L <- split(seq_p, factor(clusters))

mat <- t(sapply(L,
                FUN = function(v) {
                  summary(as.vector(C[v,v]))
                }))

mat[, "Mean"]
```

### Stars selection  
```{r}
mb_out      <- neighbor_select(data = dta, lambda_min = 1e-2, nlambda = 10, 
                               nresamples = 50, verbose = TRUE, estim_var = 0.01)
lambda1     <- mb_out$lambda_opt
#0.3525136
```

### Neighborhood selection  
This step is not needed. MGLasso wit $\lambda_2 = 0$ is theoretically equivalent to Meinshausen-Bühlmann neighborhood selection.
```{r}
mb_dta <- glasso(cov(scale(dta)),
                 rho = lambda1,
                 approx = TRUE)
```

### MGLasso  
```{r eval = FALSE}
pen_params <- seq_l2_l1_fixed(dt = dta, l1 = lambda1, nl2 = 4, l2_max = TRUE) 

system.time(mgl_amgut <- lapply(pen_params, 
                                FUN = mglasso_pair_param, 
                                X_ = dta, 
                                type = "initial"))
```

```{r eval = FALSE}
save(mgl_amgut, 
     file = paste0(path_real_data, "mgl_amgut_dta_se.RData"))
```

### Adjacency matrices
```{r}
image(as(adj_mat(mb_dta$wi), "sparseMatrix"), sub = "MB", xlab = "", ylab = "")
image(as(adj_mat(glasso_dta$wi), "sparseMatrix"), sub = "GLasso", xlab = "", ylab = "")

image(as(adj_mat(mgl_amgut$`1`$selected_Theta), "sparseMatrix"), sub = "MGLasso tv0", xlab = "", ylab = "")
image(as(adj_mat(mgl_amgut$`2`$selected_Theta), "sparseMatrix"), sub = "MGLasso tv5", xlab = "", ylab = "")
image(as(adj_mat(mgl_amgut$`3`$selected_Theta), "sparseMatrix"), sub = "MGLasso tv10", xlab = "", ylab = "")
image(as(adj_mat(mgl_amgut$`4`$selected_Theta), "sparseMatrix"), sub = "MGLasso tv15", xlab = "", ylab = "")
```

### Confusion matrix
```{r}
library(caret)

ref_mb <- adj_mat(mgl_amgut$`1`$selected_Theta)
ref_mb <- factor(as.vector(ref_mb))

pred_mglasso <- adj_mat(mgl_amgut$`2`$selected_Theta)
pred_mglasso <- factor(as.vector(pred_mglasso))

confusionMatrix(data = pred_mglasso, reference = ref_mb)
```

### Clusters  
```{r}
get_min_different_from_zero <- function(mdat) {
  mdat <- abs(mdat)
  mdat[mdat == 0] <- Inf
  return(min(mdat))
}

min_val <- get_min_different_from_zero(mgl_amgut$`2`$selected_Theta)

clusters_tv5 <- get_clusters_mgl(mgl_amgut$`2`$selected_Theta, min_val, ncol(dta))
# absolute minimum which is different from 0
```

Adjacency graph $\lambda_2 = 0$
```{r}
image(as(adj_mat(mgl_amgut$`1`$selected_Theta[order(clusters_tv5), order(clusters_tv5)]), "sparseMatrix"), sub = TeX(r'($\lambda_2 = 0$)'), xlab = "", ylab = "")
```

Adjacency graph $\lambda_2 = 5$
```{r}
adj_matrix <- as(adj_mat(mgl_amgut$`2`$selected_Theta), "sparseMatrix")

image(adj_matrix[order(clusters_tv5), order(clusters_tv5)], sub = TeX(r'($\lambda_2 = 5$)'), xlab = "", ylab = "")
```


